```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# GitHub API

[GitHub](https://github.com/) is the most famous web-based source code hosting service in the world. Millions of developers choose GitHub to host their public code repositories. Many R packages are hosted by GitHub too.

In addition to the rich features it provides in project development and collaboration, GitHub also opens its [API](https://api.github.com/) for developers to query the meta-data of users and repos. For example, we can directly get the following data:

- [My public profile on GitHub](https://api.github.com/users/renkun-ken)
- [Profile of rlist package](https://api.github.com/repos/renkun-ken/rlist)
- [All my repos on GitHub](https://api.github.com/users/renkun-ken/repos)

If you visit the links in your web browser, you will see the data presented in JSON format.

To make the data exploration more interesting, in the following examples we will explore [Hadley Wickham](https://github.com/hadley)'s GitHub data with functions provided in rlist and see how rlist makes it easier to work with such non-tabular data structures.

```{r}
library(rlist)
library(pipeR)
repos <- "https://api.github.com/users/hadley/repos?per_page=100&page=%d" %>>%
  sprintf(1:5) %>>%
  list.map(list.load(., type = "json")) %>>%
  list.takeWhile(length(.) > 0L) %>>%
  list.ungroup
```
