```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# Input/Output

rlist provides various mechanisms for list data input and output. 

## list.parse

`list.parse()` is used to convert an object to list. For example, this function can convert `data.frame`, `matrix` to a list with identical structure.

```{r}
library(rlist)
df1 <- data.frame(name=c("Ken","Ashley","James"),
  age=c(24,25,23), stringsAsFactors = FALSE)
str(list.parse(df1))
```

This function also parses JSON or YAML format text.

```{r}
jsontext <- '
[{ "name": "Ken", "age": 24 },
 { "name": "Ashley", "age": 25},
 { "name": "James", "age": 23 }]'
str(list.parse(jsontext, "json"))
```

```{r}
yamltext <- "
p1:
  name: Ken
  age: 24
p2:
  name: Ashley
  age: 25
p3:
  name: James
  age: 23
"
str(list.parse(yamltext, "yaml"))
```

## list.stack

`list.stack()` reverses `list.parse()` on a data frame, that is, it converts a list of homogeneous elements to a data frame with corresponding columns. In other words, the function stacks all list elements together, resulting in a data frame.

```{r}
jsontext <- '
[{ "name": "Ken", "age": 24 },
 { "name": "Ashley", "age": 25},
 { "name": "James", "age": 23 }]'
data <- list.parse(jsontext, "json")
list.stack(data)
```

Note that data frame is much more efficient to store tabular data that has different columns, each of which is a vector storing values of the same type. In R, a data frame is in essence a list of vectors. However, the data rlist functions are designed to deal with can be non-tabular to allow more flexible and more loose data structure.

If we are sure about the data structure of the resulted list and want to convert it to a data frame with equivalent structure, `list.stack()` does the work.

## list.load, list.save

`list.load()` loads data from a JSON, YAML, RData, or RDS file. Its default behavior is to first look at file extension and then determine which data loader is used. If the file extension does not match JSON or YAML, it will use RData loader.

`list.save()` saves a list to a JSON, YAML, RData, or RDS file. Its default behavior is similar with that of `list.load()`.

If the data are read or written by these two functions in JSON or YAML format, the data will be text-based and thus friendly for human reader. However, if a list contains complex objects such as S4 objects and language objects, the text-based format may not be appropriate to store such objects. You should consider storing them in binary format, i.e. RData or RDS file.

> NOTE: RData file is created by `save()` and can be loaded by `load()`. It usually stores an environment in which multiple objects are binded. RDS file is created by `saveRDS()` and can be loaded by `readRDS()`. It usually stores an R object directly.

`list.load()` in the latest version supports loading files specified by a character vector. It also supports loading files without file extensions by iteratively loading files by JSON and YAML loader.

## list.serialize, list.unserialize

Serialization is the process that stores an object into fully-recoverable data format. `list.serialize()` and `list.deserialize()` provides the mechanism to capitalize the R native serializer/unserializer and JSON serializer/unserializer provided by `jsonlite`.
