```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# Joining

`list.join()` joins two lists by certain expressions and `list.merge()` merges a series of named lists.

```{r}
library(rlist)
library(pipeR)
people <- list.load("http://renkun.me/rlist-tutorial/data/sample.json") %>>%
  list.names(Name)
```


## list.join

`list.join()` is used to join two lists by a key evaluated from either a common expression for the two lists or two separate expressions for each list.

```{r}
newinfo <-
  list(
    list(Name="Ken", Email="ken@xyz.com"),
    list(Name="Penny", Email="penny@xyz.com"),
    list(Name="James", Email="james@xyz.com"))
str(list.join(people, newinfo, Name))
```

## list.merge

`list.merge()` is used to recursively merge a series of lists with the later always updates the former. It works with two lists, as shown in the example below, in which a revision is merged with the original list.

More specifically, the merge works in a way that lists are partially updated, which allows us to specify only the fields we want to update or add for a list element, or use `NULL` to remove a field.

```{r}
rev1 <-
  list(
    Ken = list(Age=25),
    James = list(Expertise = list(R=2, Cpp=4)),
    Penny = list(Expertise = list(R=2, Python=NULL)))
str(list.merge(people,rev1))
```

The function also works with multiple lists. When the second revision is obtained, the three lists can be merged in order.

```{r}
rev2 <-
  list(
    James = list(Expertise=list(CSharp = 5)),
    Penny = list(Age = 24,Expertise=list(R = 3)))
str(list.merge(people,rev1, rev2))
```

Note that `list.merge()` only works with lists with names; otherwise the merging function will not know the correspondence between the list elements to merge.
