```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# Lambda expression

Although the fields of each list element are directly accessible in the expression, sometimes we still need to access the list element itself, usually for its meta-information. Lambda expressions provide a mechanism that allows you to use default or customized meta-symbols to access the meta-information of the list element.

In rlist package, all functions that work with expressions support the following types of lambda expressions.

- Implicit lambda expression: An ordinary expression with no special syntax yet the fields of elements are directly accessible. 
- Explicit lambda expression:
    - Univariate lambda expression: In contrast to implicit lambda expression, the symbol that refers to the element is customized in the following formats:
        * `x ~ expression`
        * `f(x) ~ expression`
    - Multivariate lambda expression: In contrast to univariate lambda expression, the symbols of element, index, and member name are customized in the following formats:
        * `f(x,i) ~ expression`
        * `f(x,i,name) ~ expression`

```{r}
library(rlist)
```


## Implicit lambda expression

Implicit lambda expression is an ordinary expression with no special syntax like `~`. In this case, meta symbols are implicitly defined in default, that is, `.` represents the element, `.i` represents the index, and `.name` represents the name of the element.

For example,

```{r}
x <- list(a=list(x=1,y=2),b=list(x=2,y=3))
list.map(x,y)
list.map(x,sum(as.numeric(.)))
```

In the second mapping above, `.` represents each element. For the first member, the meta-symbols take the following values:

```r
. = x[[1]] = list(x=1,y=2)
.i = 1
.name = "a"
```

## Explicit lambda expression

To use other symbols to represent the metadata of a element, we can use explicit lambda expressions.

```{r}
x <- list(a=list(x=1,y=2),b=list(x=2,y=3))
list.map(x, f(item,index) ~ unlist(item) * index)
list.map(x, f(item,index,name) ~ list(name=name,sum=sum(unlist(item))))
```

For unnamed vector members, it is almost necessary to use lambda expressions.

```{r}
x <- list(a=c(1,2),b=c(3,4))
list.map(x,sum(.))
list.map(x,item ~ sum(item))
list.map(x,f(m,i) ~ m+i)
```

For named vector members, their name can also be directly used in the expression.

```{r}
x <- list(a=c(x=1,y=2),b=c(x=3,y=4))
list.map(x,sum(y))
list.map(x,x*y)
list.map(x,.i)
list.map(x,x+.i)
list.map(x,f(.,i) ~ . + i)
list.map(x,.name)
```

*Note that `list.select` does not support explicit lambda expressions.*
