```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# List environment

List environment is an alternative construct designed for easier command chaining. `List()` function wraps a list within an environment where almost all functions in this package are defined but result in the next List environment for further operations.

Suppose we work with the following list.

```{r}
library(rlist)
library(pipeR)
people <- list.load("https://renkun-ken.github.io/rlist-tutorial/data/sample.json")
```

To create a `List environment`, run

```{r}
m <- List(people)
```

then we can operate the environment-based object `m` with `map()`, `filter()` and other functions, or extract the inner data with `m$data`. All inner functions return `List environment`, which facilities command chaining.

For example, map each member to their name.

```{r}
m$map(Name)
```

Note that the resulted object is also a `List environment` although its printed results include the inner data. To use the result with external functions, we need to extract the inner data by calling `m$data`.

Get all the possible cases of interests for those whose R experience is longer than 1 year.

```{r}
m$filter(Expertise$R > 1)$
  cases(Interests)$
  data
```

Calculate an integer vector of the average number of years using R for each interest class.

```{r}
m$class(Interests)$
  map(case ~ length(case))$
  call(unlist)$
  data
```

A more handy way to extract `data` from the List environment is to use `[]`.

```{r}
m$class(Interests)$
  map(case ~ length(case))$
  call(unlist) []
```

