```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# Misc functions

rlist provides miscellaneous functions to assist data manipulation. These functions are mainly designed to alter the structure of an list object.

## list.append, list.prepend

`list.append()` appends an element to a list and `list.prepend()` prepends an element to a list.

```{r}
library(rlist)
list.append(list(a=1, b=1), c=1)
list.prepend(list(b=1, c=2), a=0)
```

The function also works with vector.

```{r}
list.append(1:3, 4)
list.prepend(1:3, 0)
```

The names of the vector can be well handled.

```{r}
list.append(c(a=1,b=2), c=3)
list.prepend(c(b=2,c=3), a=1)
```

## list.reverse

`list.reverse()` simply reverses a list or vector.

```{r}
list.reverse(1:10)
```

## list.sample

```{r}

```

## list.zip

```{r}

```


## list.rbind, list.cbind

```{r}

```


## list.stack

```{r}

```


## list.flatten

```{r}

```


## list.names

```{r}

```

