```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=FALSE, comment='#', fig.align = 'center', results='markup')
```

# Updating

`list.update()` partially modifies the given list by a number of lists resulted from expressions.

First, we load the data without any modification.

```{r}
library(rlist)
library(pipeR)
people <- list.load("http://renkun.me/rlist-tutorial/data/sample.json")
people %>>%
  list.select(Name, Age) %>>%
  list.stack
```

`list.stack()` converts a list to a data frame with equivalent structure. We will introduce this function later.

Suppose we find that the age of each people is mistakenly recorded, say, 1 year less than their actual ages, respectively, we need to update the original data by refresh the age of each element.

```{r}
people %>>%
  list.update(Age = Age + 1) %>>%
  list.select(Name, Age) %>>%
  list.stack
```

`list.update()` can also be used to exclude certain fields of the elements. Once we update the fields we want to exclude to `NULL`, those fields are removed.

```{r}
people %>>%
  list.update(Interests = NULL, Expertise = NULL, N = length(Expertise)) %>>%
  list.stack
```
